Visual proteomics using whole-lamella 2D template matching

### 2022-03-03 figures/example-figure3.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{25cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (17.0,9.35) {}; 
\node[labelNode] {Q};
\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
\node[titleNode] {Eucentric Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (15,9.35) {}; 
\node[labelNode] {D};
\node[titleNode] {Fringe-free Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,4.85) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{16.5cm} 
    \newcommand{\figheight}{9cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,8.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/movement_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (8.5,8.35) {}; 
\node[labelNode] {B};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/thickness_by_intensity_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/example-figure4.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{25cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (17.0,9.35) {}; 
\node[labelNode] {Q};
\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
\node[titleNode] {Eucentric Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (15,9.35) {}; 
\node[labelNode] {D};
\node[titleNode] {Fringe-free Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,4.85) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{13cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,12.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer000.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};
\node (anchor) at (6.5,12.35) {}; 
\node[labelNode] {B};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer001.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};
\node (anchor) at (11,12.35) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer002.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};
\node (anchor) at (15.5,12.35) {}; 
\node[labelNode] {D};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer003.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,6.5) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer005.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};
\node (anchor) at (5,6.5) {}; 
\node[labelNode] {F};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer006.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};
\node (anchor) at (9.5,6.5) {}; 
\node[labelNode] {G};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer007.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};
\node (anchor) at (14.5,6.5) {}; 
\node[labelNode] {H};
\node[graphicNode] {\includegraphics[height=5.2cm]{content/images/slicer008.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/initmatching.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{25cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (17.0,9.35) {}; 
\node[labelNode] {Q};
\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
\node[titleNode] {Eucentric Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (15,9.35) {}; 
\node[labelNode] {D};
\node[titleNode] {Fringe-free Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,4.85) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{19cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[height=9cm]{content/images/the_lamella.png}};

\node[annotNode] at (3.5,8.35) {\contour{white}{Nuc}};
\node[annotNode] at (1.75,4.0) {\contour{white}{Nuc}};

\node[annotNode] at (3.2,4.7) {\contour{white}{M}};
\node[annotNode] at (2.75,2.25) {\contour{white}{M}};

\node[annotNode] at (1.5,8.0) {\contour{white}{GrCyt}};
\node[annotNode] at (4.5,3.5) {\contour{white}{GrCyt}};

\node (rect) at (1.1,7.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
\node[mnNode, color=blue!60] {\contour{white}{2}};

\node (rect) at (3.2,7.3) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
\node[mnNode, color=blue!60] {\contour{white}{0}};

\node (rect) at (4.5,6.25) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=red] {};
\node[mnNode, color=red] {\contour{white}{506}};

\node (rect) at (3.4,5.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
\node[mnNode, color=blue!60] {\contour{white}{16}};

\node (rect) at (2.75,3.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=green] {};
\node[mnNode, color=green] {\contour{white}{30}};

\node (rect) at (2.65,2.35) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=orange] {};
\node[mnNode, color=orange] {\contour{white}{17}};

\node (rect) at (1.25,1.5) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=blue!60] {};
\node[mnNode, color=blue!60] {\contour{white}{8}};

\node (rect) at (4.0,2.2) [anchor=center,draw,thick,minimum width=0.85cm,minimum height=0.6cm,color=magenta] {};
\node[mnNode, color=magenta] {\contour{white}{52}};

\node (anchor) at (6.5,9.35) {}; 
\node[labelNode] {B};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/30_matches.png}};
\node (n3) [box=green, fit=(img)] {};

\node (anchor) at (12.75,9.35) {}; 
\node[labelNode] {C};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/506_matches.png}};
\node (n3) [box=red, fit=(img)] {};

\node (anchor) at (6.5,4.75) {}; 
\node[labelNode] {D};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/17_matches.png}};
\node (n3) [box=orange, fit=(img)] {};

\node (anchor) at (12.75,4.75) {}; 
\node[labelNode] {E};
\node (img) [graphicNode]  {\includegraphics[height=4cm]{content/images/52_matches.png}};
\node (n3) [box=magenta, fit=(img)] {};

%%\iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/lamella_spatial_info.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \node (anchor) at (0.5,8.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/movement_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (8.5,8.35) {}; 
\node[labelNode] {B};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/thickness_by_intensity_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

>>>>

    \node (anchor) at (0.5,8.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_defocus_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,4.35) {}; 
\node[labelNode] {B};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_astigmatism_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (8.5,8.35) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/code/img/defocus_angle_vs_bs_plot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 figures/matching.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{25cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (17.0,9.35) {}; 
\node[labelNode] {Q};
\node[graphicNode] {\includegraphics[width=5cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
\node[titleNode] {Eucentric Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/fringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (15,9.35) {}; 
\node[labelNode] {D};
\node[titleNode] {Fringe-free Focus};
\node[graphicNode] {\includegraphics[height=3.0cm]{content/images/nofringebeam.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (11.5,4.85) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=4.3cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{16cm} 
    \newcommand{\figheight}{13cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=7.5cm]{content/images/screenie.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

### 2022-03-03 manuscript.tex
Workflow figure [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a4570afcb2725b9980fa97358516050b0a2697d3/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1925656087

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/00311ccf9074082904cef550d9b63ff61297b3c1/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/00311ccf9074082904cef550d9b63ff61297b3c1}{jojoelfe/deco\_lace\_template\_matching\_manuscript@00311cc}
on March 2, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a4570afcb2725b9980fa97358516050b0a2697d3/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a4570afcb2725b9980fa97358516050b0a2697d3}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a4570af}
on March 3, 2022.
